Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Really into opinion territory: s/their/her/
I default to the feminine pronouns in my own writing. I definitely grimace at
"their". But there's no obviously great resolution for this issue.
Fix spelling: s/WebRqTC/WebRTC/
Maybe capitalize full sentences in list?
Not sure at all, but my inclination is to say that full sentences should be
capitalized as such.

The PeerJS client library also provides a default signaling mechanism
that is designed to operate with a PeerJS signaling server. This is
particularly helpful because much of the WebRTC signaling transport
and protocol is not defined as part of the WebRTC standardization
effort. %TODO/CITE
The PeerJS organization provides a cloud-hosted version of a PeerJS
compatible signaling server, however an application developer can also
run their own signaling service using PeerJS PeerServer.

@@

In the Raft over WebRqTC implementation each local browser is a client
of the Raft cluster. However in Raft, the leader node is the only node
that adds entries to the log so clients on follower nodes must have
a way to communicate with the leader. This is implemented as a pair of
functions named \texttt{clientRequest} and
\texttt{clientRequestResponse}. The \texttt{clientRequest} function is
called by the client with the arguments of a client request RPC and
a callback function to be called once the request is completed. The
\texttt{clientRequest}/\texttt{clientRequestResponse} functions work
as follows:

\begin{enumerate}
\item the \texttt{clientRequestResponse} is registered with the local
    Raft.js implementation as the callback function anytime
    a \texttt{clientRequestResponse} RPC is received.
\item the \texttt{clientRequest} function keeps track of the current
    leader ID.  If the current leader ID is not set or this node is
    the leader then the client request RPC is sent directly to the
    local Raft node bypassing the network transport layer.  If the
    current leader ID is set then the request is sent to that node as
    a normal RPC request over the WebRTC channel.
\item when the \texttt{clientRequestResponse} function is called and
    the status is ``NOT\_LEADER" then the current leader ID being
    tracked by the \texttt{clientRequest} function is set to the
    leader ID specified in the response. Then the original request is
    re-issued over the normal WebRTC channel to the leader.
\item when the \texttt{clientRequestResponse} function is called with
    a successful status, the original callback argument of the
    \texttt{clientRequest} function is called with the results from
    the RPC response.
\end{enumerate}

>>>>

The PeerJS client library also provides a default signaling mechanism
that is designed to operate with a PeerJS signaling server. This is
particularly helpful because much of the WebRTC signaling transport
and protocol is not defined as part of the WebRTC standardization
effort. %TODO/CITE
The PeerJS organization provides a cloud-hosted version of a PeerJS
compatible signaling server, however an application developer can also
run her own signaling service using PeerJS PeerServer.

@@

In the Raft over WebRTC implementation each local browser is a client
of the Raft cluster. However in Raft, the leader node is the only node
that adds entries to the log so clients on follower nodes must have
a way to communicate with the leader. This is implemented as a pair of
functions named \texttt{clientRequest} and
\texttt{clientRequestResponse}. The \texttt{clientRequest} function is
called by the client with the arguments of a client request RPC and
a callback function to be called once the request is completed. The
\texttt{clientRequest}/\texttt{clientRequestResponse} functions work
as follows:

\begin{enumerate}
\item The \texttt{clientRequestResponse} is registered with the local
    Raft.js implementation as the callback function anytime
    a \texttt{clientRequestResponse} RPC is received.
\item The \texttt{clientRequest} function keeps track of the current
    leader ID.  If the current leader ID is not set or this node is
    the leader then the client request RPC is sent directly to the
    local Raft node bypassing the network transport layer.  If the
    current leader ID is set then the request is sent to that node as
    a normal RPC request over the WebRTC channel.
\item When the \texttt{clientRequestResponse} function is called and
    the status is ``NOT\_LEADER" then the current leader ID being
    tracked by the \texttt{clientRequest} function is set to the
    leader ID specified in the response. Then the original request is
    re-issued over the normal WebRTC channel to the leader.
\item When the \texttt{clientRequestResponse} function is called with
    a successful status, the original callback argument of the
    \texttt{clientRequest} function is called with the results from
    the RPC response.
\end{enumerate}
